The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-04-08 paper/sections/conclusion.tex
Dave Changes

SEM itself has much room for improvement. 
First, while we focus on NURBS surfaces here, the only part of SEM that is NURBS specific is the shape matching operation.
We believe there is potential to allow mixed models (models which include polygonal meshes, particles, subdivision surfaces and NURBS)
by extending the range of shape matching operations used by the algorithm. The shape matching operation itself could be improved to be material-aware 
(to better handle heterogenous materials) or to be robust to noisy data (allowing direct simulation of scanned data).
\revise{Additionally, more effort is required to ensure that the shape matching fit is optimal, which we do not provide guarantees for with our hierarchical shape matching approach. In future work we intend to explore using robust solvers or orthogonal bases for the fitting step.} \ty{more can be said here I suppose. I tried pinv() on the beam, which surprisingly worked, but it's just unpredictable since it should still fail on my very basic 2D box example. Haven't done much experimentation beyond this though, so I just write future work}
It is also interesting to consider the relationship between our error term and the orthogonality constraint proposed by~\citet{Zhang:CompDynamics:2020}. 
Their approach could be used to remove this parameter from SEM entirely.
Finally, in this paper we have focused on applying SEM to physics-based animation, and there is a significant amount of additional work needed to 
extend SEM reliably into engineering applications.

>>>>

SEM itself has much room for improvement. 
First, while we focus on NURBS surfaces here, the only part of SEM that is NURBS specific is the shape matching operation.
We believe there is potential to allow mixed models (models which include polygonal meshes, particles, subdivision surfaces and NURBS)
by extending the range of shape matching operations used by the algorithm. The shape matching operation itself could be improved to be material-aware 
(to better handle heterogenous materials) or to be robust to noisy data (allowing direct simulation of scanned data).
\revise{In future work we also intend to explore using robust solvers or orthogonal bases for the shape matching step itself.} \ty{more can be said here I suppose. I tried pinv() on the beam, which surprisingly worked, but it's just unpredictable since it should still fail on my very basic 2D box example. Haven't done much experimentation beyond this though, so I just write future work}
It is also interesting to consider the relationship between our error term and the orthogonality constraint proposed by~\citet{Zhang:CompDynamics:2020}. 
Their approach could be used to remove this parameter from SEM entirely.
Finally, in this paper we have focused on applying SEM to physics-based animation, and there is a significant amount of additional work needed to 
extend SEM reliably into engineering applications.

### 2021-04-08 paper/sections/methods.tex
update results and more typo fixes
Dave Changes

\dave{should have done Chebyshev shape matching to ensure higher order terms are orthogonal which would gaurantee exact reconstruction}

@@

Using these two distances we define a linear \emph{distance weight} using the well-known ReLU function:
\begin{equation}
\theta_i = \max \left(1.0 - \frac{d_{\text{primary}}}{\min (d_{\text{total}}, \alpha)}, 0.0\right)
\text{,}
\end{equation}
where $\alpha$ is a distance cutoff parameter, $d_{\text{primary}}$ is the primary ray length and $d_{\text{total}}$ is the total ray length. 
This distance weight~(\reffig{plot_distance_weight}) is the result of interpolating along the ray from $\clst$ to $\rhit$ (or a fixed point that depends on $\alpha$). 
These weights obey the Kronecker delta property for all parts but do not partition unity which we repair using a post-normalization step. For non-planar surfaces, $\rhit$ may lie on the same part as $\clst$. For points inside closed periodic surfaces, it is critical that the weights equal one in this case, so we set $\theta_i = 1$.

@@

Using raycasting to compute blending weights imbues our method with similar advantages to \citet{Sawhney:2020:MCG} (allowing us to 
handle intersecting geometry, geometry with gaps and to perform constructive solid geometry operations on the fly),
but allows us to use more general weighting functions and apply the appropriate behavior for intersecting parts.
The price we pay is that our weights are not $C^0$ continuous but rather Lipschitz smooth.
Perturbations in the boundaries of parts can cause bounded jumps in our distance weights. 
However, these jumps occupy an infinitesimal percentage of the volume of our object, and are easy to avoid when integrating
physical quantities, leaving our simulation unaffected.

@@

@@

We derive the mass matrix for our system from the definition of kinetic energy:
\begin{equation}
    T = \frac{1}{2}\dot{\vc{q}}^T\underbrace{\Pi^T\int_{\Omega}\bldmat\left(\refX\right)^T\shapef\left(\refX\right)^T\shapef\left(\refX\right)\bldmat\left(\refX\right)d\Omega\Pi}_{\MM}\dot{\vc{q}},
\end{equation}
% \begin{equation}
% T = \frac{1}{2}\int_{ \Omega} \rho \dot{\mathbf{x}}^T\dot{\mathbf{x}} d\Omega
% \text{,}
% \end{equation}
% where $\Omega$ is the 3D integration domain, $\rho$ is the density, and $\dot{\mathbf{x}}$ is the velocity for some point in the domain. Using the deformation map defined in \ref{eqn:compact_x_map}, we may rewrite this kinetic energy as
% \begin{equation}
% \begin{split}
% T & = \frac{1}{2}\int_{ \Omega} \rho \dot{\mathbf{q}}^T \mathbf{J}^T\mathbf{Y(X)}^T\mathbf{Y(X)}\ d\Omega \\
%   & = \frac{1}{2} \dot{\mathbf{q}}^T \mathbf{J}^T \left[ \int_{ \Omega} \rho \mathbf{Y(X)}^T\mathbf{Y(X)} d\Omega \right] \mathbf{J}\dot{\mathbf{q}} \\
%   & = \frac{1}{2} \dot{\mathbf{q}}^T \mathbf{M} \dot{\mathbf{q}}
% \end{split}
% \text{.}
% \end{equation}
% The second line is a result of the fact that all terms except for $\mathbf{Y(X)}$ are spatially constant, allowing us to move these outside the volume integral, which enables fast assembly of the mass matrix, $\mathbf{M}$.

>>>>

\revise{Note that hierarchical is not guaranteed to find the optimal polynomial fit and potentially risks overfitting to low-order terms.
        However we find that it provides qualitatively resonable results and avoids much of the dense matrix arithmatic and singular value decompositions 
        of alternative methods such as the Moore-Penorse inverse or QR factorization.}

@@

Using these two distances we define a linear \emph{distance weight} using the well-known ReLU function:
\begin{equation}
\theta_i = \max \left(1.0 - \frac{d_{\text{primary}}}{\min (d_{\text{total}}, \alpha)}, 0.0\right)
\text{,}
\label{eq:RELU}
\end{equation}
where $\alpha$ is a distance cutoff parameter, $d_{\text{primary}}$ is the primary ray length and $d_{\text{total}}$ is the total ray length. 
This distance weight~(\reffig{plot_distance_weight}) is the result of interpolating along the ray from $\clst$ to $\rhit$ (or a fixed point that depends on $\alpha$). 
These weights obey the Kronecker delta property for all parts but do not partition unity which we repair using a post-normalization step. For non-planar surfaces, $\rhit$ may lie on the same part as $\clst$. For points inside closed periodic surfaces, it is critical that the weights equal one in this case, so we set $\theta_i = 1$.

@@

Using raycasting to compute blending weights imbues our method with similar advantages to \citet{Sawhney:2020:MCG} (allowing us to 
handle intersecting geometry, geometry with gaps and to perform constructive solid geometry operations on the fly),
but allows us to use more general weighting functions and apply the appropriate behavior for intersecting parts.
The price we pay is that our weights are not $C^0$ continuous but rather contain bounded jumps. 
However, these jumps occupy an infinitesimal percentage of the volume of our object, and are easy to avoid when integrating
physical quantities, leaving our simulation unaffected.

@@

\revise{Note that this approach yields compactly supported weight functions due to the cut-off parameter~(Eq.~8). 
Depending on this value, we obtain a range of system matrix sparsity patterns -- from fully dense to block sparse~(Fig.~9). 
Importantly, unlike other boundary-only approaches, our method is not guaranteed to produce dense system matrices.}

@@

We derive the mass matrix for our system from the definition of kinetic energy:
\begin{equation}
    T = \frac{1}{2}\dot{\vc{q}}^T\underbrace{\Pi^T\int_{\Omega} \revise{\rho}\bldmat\left(\refX\right)^T\shapef\left(\refX\right)^T\shapef\left(\refX\right)\bldmat\left(\refX\right)d\Omega\Pi}_{\MM}\dot{\vc{q}}.
\end{equation}

% \begin{equation}
% T = \frac{1}{2}\int_{ \Omega} \rho \dot{\mathbf{x}}^T\dot{\mathbf{x}} d\Omega
% \text{,}
% \end{equation}
% where $\Omega$ is the 3D integration domain, $\rho$ is the density, and $\dot{\mathbf{x}}$ is the velocity for some point in the domain. Using the deformation map defined in \ref{eqn:compact_x_map}, we may rewrite this kinetic energy as
% \begin{equation}
% \begin{split}
% T & = \frac{1}{2}\int_{ \Omega} \rho \dot{\mathbf{q}}^T \mathbf{J}^T\mathbf{Y(X)}^T\mathbf{Y(X)}\ d\Omega \\
%   & = \frac{1}{2} \dot{\mathbf{q}}^T \mathbf{J}^T \left[ \int_{ \Omega} \rho \mathbf{Y(X)}^T\mathbf{Y(X)} d\Omega \right] \mathbf{J}\dot{\mathbf{q}} \\
%   & = \frac{1}{2} \dot{\mathbf{q}}^T \mathbf{M} \dot{\mathbf{q}}
% \end{split}
% \text{.}
% \end{equation}
% The second line is a result of the fact that all terms except for $\mathbf{Y(X)}$ are spatially constant, allowing us to move these outside the volume integral, which enables fast assembly of the mass matrix, $\mathbf{M}$.

### 2021-04-08 paper/sections/related.tex
Dave Changes

>>>>

\revise{
\emph{Embedded Methods} attempt to sidestep many of these issues by enclosing complex surface geometry inside a simulation coarse mesh~\cite{10.5555/1009379.1009573}. 
However, producing an appropriate mesh embedding introduces a number of challenges since the coarse mesh's connectivity must mirror that of the embedded surface.
This necessitates the use of complex hierarchical methods like that of~\citet{10.1145/1531326.1531358}, which themselves require the user to correctly intuit an appropriate ultimate grid resolution.
Alternately one can introduce cut cell~\cite{Tao:Mandoline:2019} or extended Finite Element~\cite{10.1145/3355089.3356576} approaches which bring with them complicated geometric operations. 
Furthermore when the DOFs do not lie on the boundary, methods such as Nitsche's Method ~\cite{Nitsche1971berEV} are required for handling Dirichlet boundary conditions. 
Our method inherits shape connectivity directly from the boundary input, avoiding these difficulties entirely.
}

### 2021-04-08 paper/sections/results.tex
Dave Changes

\revise{We perform a basic scalability test shown in \reffig{scalability} by iteratively adding more degrees of freedom to a model and measuring average runtime of a simulation step, and report the ratio of number of nonzeros in the stiffness matrix. We begin with a unit cube composed of 6 parts and on each iteration we extend the cube, adding 4 more parts. The raycasting quadrature is updated on each iteration so that a constant number of samples (45 in this case) lie in each cube. This represents a best case scenario in which sparsity is maximized as the number of degrees of freedom increases. As performance is tied to sparsity of the stiffness matrix, we see reasonable growth in the reported times, despite minimal effort on optimizing performance. This experiment was performed using a AMD Ryzen 2600 with 16GB of RAM}

>>>>

\revise{\reffig{scalability} shows a scalability study in which a  unit cube, composed of 6 parts, is extended by appending 4 more parts at a time.
Note that our algorithm scales similarly to standard high-order finite element approaches due to the compact support of our weight functions. 
This experiment was performed using a AMD Ryzen 2600 with 16GB of RAM}
